### 2019-11-19 thesis.tex
*** empty log message ***

In a first approximation, the plasma dynamics is described by the
Boltzmann equation
\begin{equation}
\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
+{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
 +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{coll}.
\label{boltz}
\end{equation}

Above, in the left-hand side, the differential vector operators $\nabla_{\bf r}$
and $\nabla_{\bf v}$ represent, respectively, gradients in space ($x,y,z$) and
velocity ($v_x, v_y,v_z$) coordinates. The quantity ${\bf F}$ is the acting
force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
$\alpha$, which in a fully ionized plasma can assume two values: electrons
$\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
variation of the velocity distribution function due to collisional interactions
between the system's particles.

For plasmas, in the general case, the acting force in Eq. \eqref{boltz}, is
given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, ${\bf E}$
and ${\bf B}$ are the electric and magnetic fields, respectively, and $c$ is
the speed of light.

\section{The Vlasov approach}
\label{vlasov-appr}

As mentioned before, in the absence of collisions, the plasma
dynamics is given by the Vlasov-Maxwell system, which is composed
of the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{q_{\alpha}}{m_{\alpha}}
  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
\end{equation}
where the fields are described by the Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t},
\end{eqnarray}
here given in cgs units, as commonly used in the
;plasma physics literature.

>>>>

In a first approximation, the plasma dynamics is described by the
Boltzmann equation
\begin{equation}
\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
+{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
 +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{\rm coll}.
\label{boltz}
\end{equation}

Above, on the left-hand side, the differential vector operators $\nabla_{\bf r}$
and $\nabla_{\bf v}$ represent, respectively, the gradients in ($x,y,z$) space
and ($v_x, v_y,v_z$) velocity coordinates. The quantity ${\bf F}$ is the acting
force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
$\alpha$, which, in a fully ionized plasma, can assume two values: electrons
$\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
variation of the velocity distribution function due to collisional interactions
between the system's particles.

For plasmas, in the general case, the acting force in Eq. \eqref{boltz}, is
given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, $c$ is
the speed of light, and ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$ are
the electric and magnetic fields, respectively.

Collisional interactions can be neglected when the time necessary for
the plasma to establish statistical equilibrium - the relaxation time
$\tau_{\rm rel}$ - is much greater than the characteristic time $\tau$
of the process being studied~\cite{klimon,Tigik2015}.
% The relaxation time of a plasma is defined
% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
% is the plasma parameter.

\section{Vlasov-Maxwell system of equations}
\label{vlasov-maxwell}
As mentioned before, in the absence of collisions, the plasma dynamics is given
by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{q_{\alpha}}{m_{\alpha}}
  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
\end{equation}
where the fields are described by the Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
\end{eqnarray}
% here given in cgs units, as commonly used in the plasma physics literature.
